%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[letterpaper]{deedy-resume} % Use US Letter paper, change to a4paper for A4
\begin{document}
%----------------------------------------------------------------------------------------
% TITLE SECTION
%----------------------------------------------------------------------------------------
\lastupdated % Print the Last Updated text at the top right
\namesection{Ashish}{Gupta}{ % Your name
\urlstyle{same}\url{www.ashmew2.me} \\ % Your website, LinkedIn profile or other web address
\href{mailto:ashmew2@gmail.com}{ashmew2@gmail.com} | +31 682668392 % Your contact information
}
%----------------------------------------------------------------------------------------
% LEFT COLUMN
%----------------------------------------------------------------------------------------
\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page
%------------------------------------------------
% Education
%------------------------------------------------
\section{Education}
\subsection{Pune University}
\descript{BE in Information Technology}
\location{Graduated May 2015 | Pune, IN}
Pune Institute of Computer Technology \\
\sectionspace % Some whitespace after the section
%------------------------------------------------
% Links
%------------------------------------------------
\section{handles}
Github - \href{https://github.com/ashmew2}{\bf ashmew2} \\
Freenode IRC - \href{http://freenode.org} {\bf ashmew2} \\
CodeForces - \href{http://codeforces.com/profile/ashmew2}{\bf ashmew2} \\
Linkedin - \href{in.linkedin.com/in/ashmew2/} {\bf ashmew2} \\
Ubuntu Forums - \href{http://ubuntuforums.org/showthread.php?t=821461} {\bf ashmew2} \\
KolibriOS Forums - \href{http://board.kolibrios.org/memberlist.php?mode=viewprofile&u=6211} {\bf ashmew2} \\
CodeChef - \href{http://www.codechef.com/users/ashmew2}{\bf ashmew2} \\
\sectionspace % Some whitespace after the section
%------------------------------------------------
% Coursework
%------------------------------------------------
\section{Coursework}
\subsection{UnderGraduate}
Algorithms and Data Structures \\
Discrete Structures \\
Advanced Operating Systems \\
Compiler Design \\
Advanced Computer Networks \\
Distributed Systems \\
\sectionspace % Some whitespace after the section
%------------------------------------------------
% Skills
%------------------------------------------------
\section{Skills}
\subsection{Programming}
C \textbullet{} C++ \textbullet{} Python \textbullet{} Emacs Lisp\\
BASH \textbullet{} i386 Assembly \\
Click Modular Router  \textbullet{} GNU Make \\
\sectionspace % Some whitespace after the section
\subsection{TECHNOLOGY / TOOLS}
Emacs \textbullet{} Git \textbullet{} SVN  \textbullet{} Wireshark \\
GNU / Linux \textbullet{} Mercurial \textbullet{}
IRC \textbullet{}  
\sectionspace % Some whitespace after the section
\subsection{Interests}
Free and Open Source Software \\
GNU / Linux \\
Problem Solving \\
Distributed Systems \\
Operating Systems and Kernels\\
Networks \\
Multiplayer Gaming \\
Protocol Design \\
Physics \\
Mathematics \\
\sectionspace % Some whitespace after the section

%----------------------------------------------------------------------------------------
\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
% RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page
%------------------------------------------------
% Experience
%------------------------------------------------
\section{EXPERIENCE}
\runsubsection{Optiver}
\descript{| Nov 2016 - Present}
\location{Amsterdam, Netherlands}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item Engineer in Core Systems \\
\end{tightitemize}
\sectionspace % Some whitespace after the section
%------------------------------------------------
\runsubsection{Rakuten Inc}
\descript{| Oct 2015 - Oct 2016}
\location{Tokyo, Japan}
\begin{tightitemize}
\item Core API Developer for Rakuten Super Point \\
\item end-to-end pipelines with Ruby, Shell and Python \\
\end{tightitemize}
\sectionspace % Some whitespace after the section
%------------------------------------------------
\section{Open Source Contributions}
\runsubsection{Wireless Mesh Networks}
\descript{| Dec 2014 - Mar 2015}
\location{Bandwidth utilization in Wireless Mesh Networks}
\begin{tightitemize}
\item Use multiple internet connections simultaneously for increased throughput.
\item Load balancing in Userspace using Click Modular Router for linear gains.
\item Radio Physics, ARP, Reverse Proxies, DHCP, L2 and L3 networking.
\end{tightitemize}
\sectionspace % Some whitespace after the section
%------------------------------------------------
\runsubsection{Kolibri OS}
\descript{| Ongoing }
\location{Developer and Mentor}
\begin{tightitemize}
\item Author/Maintainer of Netsurf Web browser for KolibriOS.
\item Developed a C to Assembly Interface for using assembly libraries in C.
\item Developing a Cross Compiler based on GCC and GNU binutils with newlib port.
\item Contributions to TCP network stack, HTTP library
\item Mentor for GSoC 2016 for developing a POSIX C layer and FTP client.
\item C, assembly, opcode level debugging, newlib, toolchains, kernel
\end{tightitemize}
\sectionspace % Some whitespace after the section
%------------------------------------------------
\runsubsection{Pidgin Instant Messenger}
\descript{| May 2013 – Sep 2013}
\location{Implement File Transfer for Google Talk in in Pidgin}
\begin{tightitemize}
\item Reverse engineered the libjingle protocol used by Google Talk for file transfers.
\item Implemented the reversed libjingle into Pidgin's Google Talk Protocol plugin.
\item Documented the working of the libjingle protocol on the IM Freedom wiki.
\item C, XMPP, Networking, Protocol design, libnice, NAT traversal.
\end{tightitemize}
\sectionspace % Some whitespace after the section
%------------------------------------------------
\runsubsection{The Clash MCQ System}
\descript{| Jul 2012 – Sep 2012}
\location{A System for hosting intercollege programming competitions}
\begin{tightitemize}
\item Why waste paper when you can avoid it?
\item Python, Qt, Networking, Algorithms, Data Structures.
\end{tightitemize}
\sectionspace % Some whitespace after the section
%------------------------------------------------
% Achievements
%------------------------------------------------
\section{Achievements}
\runsubsection{ACM ICPC}
\descript{| Asia Regionals}
\location{International Collegiate Programming Challenge.}
\location{December 2012 | IIT Kanpur | All Asia Rank 54}
\location{December 2013 | ASE Bangalore| All Asia Rank 110}
\location{December 2013 | IIT Kanpur | All Asia Rank 36}
\sectionspace % Some whitespace after the section
\runsubsection{Google Summer of Code}
\descript{| GSOC}
\location {Student in 2013 for Pidgin}
\location {Student in 2014 for KolibriOS}
\location {Mentor in 2016 for KolibriOS}
%------------------------------------------------
\sectionspace % Some whitespace after the section
%----------------------------------------------------------------------------------------
\end{minipage} % The end of the right column
%----------------------------------------------------------------------------------------
% SECOND PAGE (EXAMPLE)
%----------------------------------------------------------------------------------------
%\newpage % Start a new page
%\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page
%\section{Example Section}
%\end{minipage} % The end of the left column
%\hfill
%\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page
%\section{Example Section 2}
%\end{minipage} % The end of the right column
%----------------------------------------------------------------------------------------
\end{document}
